---
title: "linear_regression"
author: "Julia Romberg"
date: "2024-07-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```
```{r, results='hide'}
library(vroom)
library(tidyverse)
library(MASS)
library(car)
```

Load the dataset that contains the set of independent variables (IV: 
socio-cultural information) and the set of dependent variables (DV: stylistic 
features). The dataset was prepared using the "lm-prep-cycle1.ipynb" file.

```{r}
data <- vroom("corpus_de_lm_1_nondummy_nomv.csv")
```

Choose meaningful reference categories to make interpretation of results easier.

```{r}
data$civil_status <- relevel(factor(data$civil_status), "Ledig")
data$denomination <- relevel(factor(data$denomination), "Konfessionslos")
data$education <- relevel(factor(data$education), "Universität")
data$rile <- relevel(factor(data$rile), "Links")
data$galtan <- relevel(factor(data$galtan), "Konservativ")
```

DV

```{r}
dv_surf <- c('FleschReadingEase', 'GunningFogIndex', 'characters_per_word',
             'words_per_sentence', 'type_token_ratio', 'long_words', 
             'complex_words')
dv_synt <- c('ADJ', 'ADP', 'ADV', 'AUX', 'CCONJ', 'DET', 'NOUN', 'NUM', 
             'PART', 'PRON', 'PROPN', 'PUNCT', 'SCONJ', 'VERB', 'X', 
             'Entities', 'pres_tense', 'imperative', 'first_person') # 'INTJ', 'SYM'
```

Run linear regression with stepwise variable selection: surface features

```{r}
for (i in dv_surf) {
  print(i)
  null_model <- lm(as.formula(paste(paste(i, "~"), "1")), data = data)
  # build model including interactions between variables
  aic_model <- stepAIC(null_model,
                       scope = list(lower = ~ 1, 
                                    upper = ~ (gender + age + residence + 
                                                 civil_status + denomination + 
                                                 education + rile + galtan)^2),
                       direction = "forward")
  # show outcome
  print(summary(aic_model))
  # check VIF for model
  print(vif(aic_model, type = 'predictor'))
}
```

Run linear regression with stepwise variable selection: syntactic features

```{r}
for (i in dv_synt) {
  print(i)
  null_model <- lm(as.formula(paste(paste(i, "~"), "1")), data = data)
  # build model including interactions between variables
  aic_model <- stepAIC(null_model,
                       scope = list(lower = ~ 1, 
                                    upper = ~ (gender + age + residence + 
                                                 civil_status + denomination + 
                                                 education + rile + galtan)^2),
                       direction = "forward")
  # show outcome
  print(summary(aic_model))
  # check VIF for model
  print(vif(aic_model, type = 'predictor'))
}
```
